Re-fit

### 2022-08-17 scripts/r/04_refit/refit_sc.Rmd
♻️ - excluded polymetme_brevirostrum
We have excluded this because of fixed-effect matrix rank deficiency
given that many combination of Condition * effect_cat do not exist
in the data.

```{r}
# Get datasets
praat_data <- read_delim("./data/analyses/sc/polymetme_brevirostrum/Data/acoustic_results.txt", delim = "\t")
norming_data <- read_csv("./data/analyses/sc/polymetme_brevirostrum/Data/ratings_summary.csv")
ratings <- read_csv("./data/osf/norming/ratings/ratings.csv")
foods <- list('aprikose','kirsche','moehre','gurke','erbsen','tomate','kartoffeln','banane','zitrone','bohnen','erdbeere','mandarine','walnuss')
# Get rid of that pesky case marking and include typicality bins
msa_data <- norming_data %>%
  filter(colour %in% list('braun','gelb','gruen','rot','orange')) %>% 
  mutate(
    object = tolower(object),
    Typicality = case_when(
      typ_median >= 90 ~ "typical",
      typ_median < 25 ~ "atypical",
      typ_median >= 25 & typ_median < 90 ~ "medium"
    ),
    colour = recode(colour, "braun"="braunen", "gelb"="gelben", "gruen"="gruenen", "rot"="roten", "orange"="orangen")
  ) %>%
  right_join(., praat_data, by = c("colour"="Adjective", "object"="Noun")) %>%
  filter(is.na(Notes)) %>%
  mutate(
    across(contains("f0"), function(x) {ifelse(x == "--undefined--", NA, x)}),
    Category = as.factor(ifelse(object %in% foods, "FOOD", "NONFOOD")),
    effect_cat = factor(Typicality, levels = c("atypical", "medium", "typical")),
    Adj_Dur = scale(Adj_Dur) %>% as.numeric(),
    Condition = as.factor(Condition),
    Category = as.factor(Category)
  )

@@

```{r}
polymetme_brevirostrum_1_dur_cat <- brm(
  Adj_Dur ~ Condition * effect_cat + effect_cat * Category + (Condition * effect_cat | Speaker) + (Condition | object) + (effect_cat | colour),
  data = msa_data,
  chains = 1,
  cores = 8,
  threads = threading(8, grainsize = 100), 
  backend = "cmdstanr",
  file = "data/analyses/models/polymetme_brevirostrum_1_dur_cat",
  seed = my_seed
)
```

>>>>

We have excluded this because of fixed-effect matrix rank deficiency given that many combination of Condition * effect_cat do not exist in the data.

```{r eval=FALSE}
# Get datasets
praat_data <- read_delim("./data/analyses/sc/polymetme_brevirostrum/Data/acoustic_results.txt", delim = "\t")
norming_data <- read_csv("./data/analyses/sc/polymetme_brevirostrum/Data/ratings_summary.csv")
ratings <- read_csv("./data/osf/norming/ratings/ratings.csv")
foods <- list('aprikose','kirsche','moehre','gurke','erbsen','tomate','kartoffeln','banane','zitrone','bohnen','erdbeere','mandarine','walnuss')
# Get rid of that pesky case marking and include typicality bins
msa_data <- norming_data %>%
  filter(colour %in% list('braun','gelb','gruen','rot','orange')) %>% 
  mutate(
    object = tolower(object),
    Typicality = case_when(
      typ_median >= 90 ~ "typical",
      typ_median < 25 ~ "atypical",
      typ_median >= 25 & typ_median < 90 ~ "medium"
    ),
    colour = recode(colour, "braun"="braunen", "gelb"="gelben", "gruen"="gruenen", "rot"="roten", "orange"="orangen")
  ) %>%
  right_join(., praat_data, by = c("colour"="Adjective", "object"="Noun")) %>%
  filter(is.na(Notes)) %>%
  mutate(
    across(contains("f0"), function(x) {ifelse(x == "--undefined--", NA, x)}),
    Category = as.factor(ifelse(object %in% foods, "FOOD", "NONFOOD")),
    effect_cat = factor(Typicality, levels = c("atypical", "medium", "typical")),
    Adj_Dur = scale(Adj_Dur) %>% as.numeric(),
    Condition = as.factor(Condition),
    Category = as.factor(Category)
  )

@@

```{r eval=FALSE}
polymetme_brevirostrum_1_dur_cat <- brm(
  Adj_Dur ~ Condition * effect_cat + effect_cat * Category + (Condition * effect_cat | Speaker) + (Condition | object) + (effect_cat | colour),
  data = msa_data,
  chains = 1,
  cores = 8,
  threads = threading(8, grainsize = 100), 
  backend = "cmdstanr",
  file = "data/analyses/models/polymetme_brevirostrum_1_dur_cat",
  seed = my_seed
)
```
